% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Conflicts},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Conflicts}
\author{}
\date{}

\begin{document}
\maketitle

{[}16/05/2023{]}\\
We come from different backgrounds which means conflict are bound to
happen among us.\\
When people are pursing incompatible goals and when people try to
achieve a single thing for only themselves, that is a recipe for
conflicts.

People don\textquotesingle t trust the government to solve conflicts as
they believe they are biased and would only favor a side they prefer
instead of finding a mutual solution to the conflict.

\textbf{Types of conflicts:}

\begin{itemize}
\tightlist
\item
  Ethnic conflicts
\item
  Sectarian/Religious conflicts
\item
  Political conflicts
\item
  Resource conflict
\end{itemize}

\textbf{Ethnics conflicts:} When politicians favor their ethnic group
when in power causing other ethnicities to hate the ruling ethnicity.

\textbf{Sectarian Conflict:} Conflicts between adherents of different
religions.

\textbf{Political Argument}: occur over the outcome of an election, it
is when accusation of rigging are thrown at the elected party.

\textbf{Resource conflict:} conflicts over a natural resource that
brings income for a particular nation/community.

\textbf{Causes of Conflicts:}

\begin{enumerate}
\tightlist
\item
  Abuse of political power
\item
  Manipulation of electoral process (rigging)
\item
  Political intolerance
\item
  Violation of right to freedom declared in the constitution.
\item
  Material deprivation/Poverty
\end{enumerate}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\textbf{Conflict Resolution:}\\
the head of the institution is responsible for resolving conflicts\\
Father = Family\\
Oba/Chief = Community\\
Government = State

Must be able to build trust of people involved in conflict, that ending
conflict is best for them.

\textbf{Concepts in resolving conflict:}

\begin{enumerate}
\tightlist
\item
  Peace Mediation
\item
  Peace Building
\item
  Peace Keeping
\end{enumerate}

\textbf{Peace mediation:} a third party offers to mediate to bring to an
end the ongoing conflict.

\textbf{Characteristics of a mediator:}

\begin{itemize}
\tightlist
\item
  Trust: Parties must have trust in the mediator, a mediator must be
  seen as unbiased by the parties
\item
  Mediator must make both parties realize that ending the conflict would
  bring about a mutual advantage for both parities.
\end{itemize}

\textbf{Peace building:} post-conflict phenomenon. After the fight, one
must take steps that ensures the fight would not break out again\\
Ways of peace-building:\\
- Encourage intermarriage\\
- Introduce intercommunal sports festivals\\
- Invitation to cultural festivals.

\textbf{Peace Keeping:} Enforcing policies to keep the peace. It is how
to make parties maintain the peace and keep to the agreement made.\\
Agreement: Peace deal / Pact

\end{document}
